{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-12-13 main.tex
small correction
B-spline basis & sim_JJ_tmp.R
Added more details to section on b-splines and saved reformatted and commented code as simulation_study_JJ_tmp.R

	\begin{multicols}{2}
		\begin{enumerate}
			\item $\langle v, v \rangle \geq 0$
			\item $\langle v, v \rangle = 0$ if $v = 0$
			\item $\langle a_1 v_1 = a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
		\end{enumerate}
	\end{multicols}

@@

	{\color{red}Explain what happens when $l+m+1 > L$ !!!}

>>>>

	\begin{multicols}{2}
		\begin{enumerate}
			\item $\langle v, v \rangle \geq 0$
			\item $\langle v, v \rangle = 0$ if $v = 0$
			\item $\langle a_1 v_1 + a_2 v_2, v \rangle = a_1 \langle v_1, v \rangle + a_2 \langle v_2, v \rangle$
			\item $\langle v_1, v_2 \rangle = \langle v_2, v_1 \rangle$
		\end{enumerate}
	\end{multicols}

@@

	This, however, does not really yield a basis of $\mathbb{L}^2$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2$. To really obtain a basis of $\mathbb{L}^2$ from B-splines, further theoretical considerations about, for example, infinite series of B-splines and specific knot choices would have to be made. As this is out of the scope of this paper, for the sake of simplicity, we will assume that a B-spline basis representation of a function in $\mathbb{L}^2$ will serve as a sufficient approximation for an appropriately chosen B-spline basis. 
	Even though, this approach is not theoretically exact, in practice, this is often a reasonable approach and yields satisfactory results in cases where the functional form of B-splines makes them an appropriate approximation tool.

	{\color{red}Explain what happens when $l+m+1 > L$ !!!\\
		Additionally, modify for multiple knots at the boundaries to get better behavior at the boundaries. Needs some more explanation.}
